Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-02 doc/manuscript/manuscript.Rmd
attempt to find solution to #17

The number of observed alleles per locus ranged from two to 10 with an average of `r signif(Amean, 3)` (Table \@ref(tab:locus-stats)).
Locus `r loc_table$Locus[loc_table$allele==2]`, which contained only 2 alleles, showed low values of both *h* (`r signif(loc_table$Hexp[loc_table$allele==2], 3)`) and evenness (`r signif(loc_table$Evenness[loc_table$allele==2], 3)`), indicating that there was one dominant allele present. 
Analysis of the haplotype accumulation curve showed no clear plateau for 11 or 16 loci (Supplemental Information), indicating that we would likely obtain more multilocus haplotypes if we were to genotype more loci.

@@

The analysis of molecular variance (AMOVA) for clone-corrected samples over the hierarchy of Region, Source, and Year showed significant variation between Regions and Years, but no significant variation between wmn and producer fields (Table \@ref(tab:amova)).
In contrast, when we compared the three cultivars, Beryl, Bunsi, and G122, we found no significant differentiation (Supplementary Information).

@@

All scripts, data, and resources used to generate the results presented in this publication (including Supplementary Information) are fully reproducible and available at The Open Science Framework https://osf.io/ejb5y.

>>>>

The number of observed alleles per locus ranged from two to 10 with an average of `r signif(Amean, 3)` (Table \@ref(tab:locus-stats)).
Locus `r loc_table$Locus[loc_table$allele==2]`, which contained only 2 alleles, showed low values of both *h* (`r signif(loc_table$Hexp[loc_table$allele==2], 3)`) and evenness (`r signif(loc_table$Evenness[loc_table$allele==2], 3)`), indicating that there was one dominant allele present. 
Analysis of the haplotype accumulation curve showed no clear plateau for 11 or 16 loci (See section on 'Loading Data and Setting Strata' in the MLG-distribution.md[^1] file in the supplemental files [@kamvar2017data]), indicating that we would likely obtain more multilocus haplotypes if we were to genotype more loci.

[^1]: Direct link: https://github.com/everhartlab/sclerotinia-366/blob/master/results/MLG-distribution.md#loading-data-and-setting-strata

@@

The analysis of molecular variance (AMOVA) for clone-corrected samples over the hierarchy of Region, Source, and Year showed significant variation between Regions and Years, but no significant variation between wmn and producer fields (Table \@ref(tab:amova)).
In contrast, when we compared the three cultivars, Beryl, Bunsi, and G122, we found no significant differentiation (See section on 'Host Differentiation' in the wmn-differentiation.md[^2] file in the supplemental files [@kamvar2017data]).

[^2]: Direct link: https://github.com/everhartlab/sclerotinia-366/blob/master/results/wmn-differentiation.md#host-differentiation

@@

All scripts, data, and resources used to generate the results presented in this publication (including Supplementary Information) are fully reproducible and available at The Open Science Framework https://osf.io/ejb5y [@kamvar2017data].
